### 2023-09-22 appendices/supplementary_retrospective.tex
Updates to table formatting retrospective

\chapter[supplementary material: a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{Supplementary Material for: A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{app:supplementary-retrospective}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

Let $z^{(n,d)}$ be the logit output of model $n$ for transcript $d$, $t^{(n)}$ be the tuned logit threshold of model $n$, and $N$ be the number of models in the ensemble. The output score $p^{(n)}$ is then given by 
%
\begin{equation}
    p^{(d)} = \frac{1}{N} \sum_{n=1}^N \sigma(z^{(n,d)} - t^{(n)}) \enspace ,
\end{equation}
%
where $\sigma(\cdot)$ is the sigmoid function (or standard logistic function). The final ensembel predction $s^{(d)}$ is then simply 
%
\begin{equation}
    s^{(d)} = I_{p^{(d)} > 0.5}(p^{(d)}) \enspace ,
\end{equation}
%
where $I_{\cdot}(\cdot)$ is the indicator function that returns 1 if the subscript condition is satisfied and 0 otherwise.

@@

% \todo[inline]{Insert table A2 here}
\begin{table}[h]
    \centering
    \caption{Model performance based on sex and age [mean (95\% CI)] when 1-1-2 training data is not used for training.}
    \label{tab_retrospective:tableA2}
    % \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{2}{c|}{Model} & \multicolumn{2}{c}{Model} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

@@

        F1-score [\%] $\uparrow$ & \makecell{28.7 \\ (27.8-29.6)} & \makecell{36.2 \\ (35.3-37.2)} & \makecell{20.5 \\ (19.5-21.5)} & \makecell{39.4 \\ (38.6-40.3)} \\
        \midrule
        Sensitivity [\%] $\uparrow$ & \makecell{58.2 \\ (56.7-59.9)} & \makecell{62.1 \\ (60.7-63.6)} & \makecell{53.0 \\ (50.9-55.0)} & \makecell{63.0 \\ (61.9-64.3)} \\
        \midrule
        PPV [\%] $\uparrow$ & \makecell{19.0 \\ (18.3-19.7)} & \makecell{25.6 \\ (24.8-26.4)} & \makecell{12.7 \\ (12.0-13.4)} & \makecell{28.7 \\ (27.9-29.5)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - NPV)}  & \makecell{0.077 \\ (0.073-0.080)} & \makecell{0.102 \\ (0.097-0.106)} & \makecell{0.034 \\ (0.032-0.036)} & \makecell{0.318 \\ (0.305-0.331)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{0.45 \\ (0.446-0.463)} & \makecell{0.483 \\ (0.473-0.494)} & \makecell{0.264 \\ (0.258-0.270)} & \makecell{1.335 \\ (1.308-1.362)} \\

        \bottomrule
    \end{tabular}%
    % }
\end{table}

% \todo[inline]{Insert table A3 here}
\begin{table}[h]
    \centering
    \caption{Model performance based on sex and age [mean (95\% CI)] on the 2021 data without diagnostic category.}
    \label{tab_retrospective:tableA3}
    % \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{2}{c|}{Model} & \multicolumn{2}{c}{Model} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

@@

        F1-score [\%] $\uparrow$                                 & \makecell{30.4 \\ (29.3-31.5)} & \makecell{35.2 \\ (34.0-36.4)} & \makecell{24.3 \\ (23.0-25.7)} & \makecell{36.6 \\ (35.6-37.6)} \\
        \midrule
        Sensitivity [\%] $\uparrow$                              & \makecell{44.5 \\ (42.9-46.0)} & \makecell{52.8 \\ (51.1-54.4)} & \makecell{45.6 \\ (43.4-47.9)} & \makecell{49.2 \\ (47.9-50.5)} \\
        \midrule
        PPV [\%] $\uparrow$                                      & \makecell{23.1 \\ (22.2-24.1)} & \makecell{26.4 \\ (25.3-27.4)} & \makecell{16.6 \\ (15.5-17.5)} & \makecell{29.1 \\ (28.2-30.0)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - NPV)}         & \makecell{0.152 \\ (0.146-0.159)} & \makecell{0.155 \\ (0.147-0.162)} & \makecell{0.058 \\ (0.055-0.062)} & \makecell{0.372 \\ (0.359-0.386)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell{0.404 \\ (0.394-0.414)} & \makecell{0.480 \\ (0.467-0.494)} & \makecell{0.246 \\ (0.239-0.254)} & \makecell{0.873 \\ (0.852-0.894)} \\

        \bottomrule
    \end{tabular}%
    % }
\end{table}

@@

\begin{table}[h]
    \centering
    \caption{Overall performance on MH-1813 test data, performance without 1-1-2 training data, and performance without 1813 training data [mean (95\% CI)].}
    \label{tab_retrospective:tableA5}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

        Call-takers  & \makecell[c]{25.8 \\ (23.7-27.9)} & \makecell[c]{52,7 \\ (49,2-56.4)} & \makecell[c]{17.1 \\ (15.5-18.6)} & \makecell[c]{0.105 \\ (0.094-0.116)} & \makecell[c]{0.565 \\ (0.539-0.590)} \\
        \midrule
        Model        & \makecell[c]{35.7 \\ (35.0-36.4)} & \makecell[c]{63.0 \\ (62.0-64.1)} & \makecell[c]{24.9 \\ (24.3-25.5)} & \makecell[c]{0.082 \\ (0.079-0.085)} & \makecell[c]{0.419 \\ (0.413-0.426)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Without 1-1-2 training data (only MH-1813 data)}} \\
        \midrule

        Model        & \makecell[c]{32.4 \\ (31.8-33.1)} & \makecell[c]{60.4 \\ (59.3-61.4)} & \makecell[c]{22.2 \\ (21.6-22.7)} & \makecell[c]{0.088 \\ (0.085-0.091)} & \makecell[c]{0.467 \\ (0.460-0.474)} \\

        \midrule
        & \multicolumn{5}{c}{\textit{Without MH-1813 training data (only 1-1-2 data)}} \\
        \midrule

        Model        & \makecell[c]{31.4 \\ (30.7-32.1)} & \makecell[c]{50.4 \\ (49.3-51.4)} & \makecell[c]{22.8 \\ (22.2-23.4)} & \makecell[c]{0.110 \\ (0.106-0.113)} & \makecell[c]{0.375 \\ (0.369-0.381)} \\

@@

% % \todo[inline]{Insert table A4 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest positive rank score in calls predicted as stroke.}
    \label{tab_retrospective:tableA6}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llccc}
        \toprule
        \multicolumn{6}{c}{Stroke predictions, $D=1,897$} \\
        \midrule
         & Word, $w$ (\textit{Danish}) & Translation (\textit{English}) & Rank, $r^{(w)}$ & Occurences, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Ambulance & Ambulance & $1.000$ & $1,$680 & $0.52 \pm 0.51$ \\
        2. & Blodprop & Blood clot & $0.599$ & $89$5 & $0.51 \pm 0.58$ \\
        3. & Venstre & Left & $0.381$ & $1,$108 & $0.38 \pm 0.4$ \\
        4. & Højre & Right & $0.326$ & $1,$050 & $0.31 \pm 0.42$ \\
        5. & Dobbeltsyn & Double vision & $0.247$ & $84$ & $1.01 \pm 1.26$ \\
        6. & Ordene & The words & $0.217$ & $34$4 & $0.6 \pm 0.45$ \\
        7. & Pludselig & Suddenly & $0.142$ & $78$3 & $0.29 \pm 0.28$ \\
        8. & Arm & Arm & $0.140$ & $70$9 & $0.3 \pm 0.3$ \\
        9. & Side & Side & $0.125$ & $1,$139 & $0.23 \pm 0.21$ \\
        10. & Apopleksi & Stroke & $0.102$ & $11$7 & $0.33 \pm 0.82$ \\
        11. & Dobbelt & Double & $0.102$ & $11$3 & $0.54 \pm 0.72$ \\
        12. & Styre & Control & $0.092$ & $13$4 & $0.63 \pm 0.46$ \\
        13. & Opkald & Call & $0.067$ & $39$ & $0.18 \pm 1.22$ \\
        14. & Følelsesløs & Numb & $0.065$ & $94$ & $0.53 \pm 0.58$ \\
        15. & Minutter & Minutes & $0.064$ & $76$3 & $0.22 \pm 0.16$ \\
        16. & Talebesvær & Difficulties speaking & $0.063$ & $44$ & $0.87 \pm 0.72$ \\
        17. & Hjerneblødning & Haemorrhagic stroke & $0.060$ & $13$3 & $0.4 \pm 0.49$ \\
        18. & Hånd & Hand & $0.057$ & $29$7 & $0.28 \pm 0.31$ \\
        19. & Ambulancen & The ambulance & $0.055$ & $52$1 & $0.21 \pm 0.23$ \\
        20. & Snøvler & Slurred speech & $0.052$ & $58$ & $0.71 \pm 0.54$ \\
        21. & Blodpropper & Blood clots & $0.051$ & $22$4 & $0.27 \pm 0.36$ \\
        22. & Hurtigt & Fast & $0.048$ & $66$3 & $0.18 \pm 0.18$ \\
        23. & Udtrykke & Express & $0.044$ & $44$ & $0.59 \pm 0.74$ \\
        24. & Blodfortyndende & Blood thinner & $0.044$ & $25$9 & $0.32 \pm 0.22$ \\
        25. & Usammenhængende & Incoherent & $0.043$ & $15$ & $1.14 \pm 1.13$ \\
        26. & Skæv & Lopsided & $0.039$ & $21$1 & $0.29 \pm 0.28$ \\
        27. & Nedsat & Reduced & $0.038$ & $52$8 & $0.14 \pm 0.21$ \\
        28. & Hænger & Hangs & $0.036$ & $62$8 & $0.15 \pm 0.17$ \\
        29. & Forbigående & Transient & $0.035$ & $48$ & $0.52 \pm 0.62$ \\
        30. & Vrøvler & Not making sense & $0.033$ & $14$ & $1.13 \pm 0.89$ \\
        \bottomrule
    \end{tabular}%
    }
\end{table}

% \todo[inline]{Insert table A5 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest negative rank score in calls predicted as non-stroke.}
    \label{tab_retrospective:tableA7}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llcrr}
        \toprule
        \multicolumn{6}{c}{Non-stroke predictions, $D=342,133$} \\
        \midrule
         & Word, $w$ (\textit{Danish}) & Translation (\textit{English}) & Rank, $r^{(w)}$ & Occurences, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Stivkrampe & Tetanus & $-1.000$ & $4378$ & $-19.40 \pm 10.61$ \\
        2. & Gravid & Pregnant & $-0.901$ & $8749$ & $-12.08 \pm 8.64$ \\
        3. & Skåret & Cut & $-0.772$ & $7592$ & $-11.98 \pm 8.61$ \\
        4. & Forbinding & Bandage & $-0.569$ & $4561$ & $-12.87 \pm 10.08$ \\
        5. & Amager & Amager (a location) & $-0.566$ & $23776$ & $-5.60 \pm 4.43$ \\
        6. & Klokken & O'clock & $-0.535$ & $94436$ & $-2.22 \pm 2.69$ \\
        7. & Skadestuen & The emergency room & $-0.486$ & $42809$ & $-3.72 \pm 3.23$ \\
        8. & Politiet & The police & $-0.413$ & $2903$ & $-10.73 \pm 13.77$ \\
        9. & Hævet & Swollen & $-0.388$ & $60559$ & $-2.84 \pm 2.38$ \\
        10. & Håndkøb & over the counter (otc) & $-0.372$ & $4641$ & $-11.64 \pm 6.00$ \\
        11. & Halsen & The neck & $-0.366$ & $30151$ & $-3.33 \pm 3.86$ \\
        12. & Feber & Fever & $-0.361$ & $112586$ & $-1.94 \pm 1.76$ \\
        13. & Recept & Prescription & $-0.334$ & $5450$ & $-9.87 \pm 5.82$ \\
        14. & Centimetre & Centimetre & $-0.311$ & $12026$ & $-6.01 \pm 4.39$ \\
        15. & Knæet & The knee & $-0.300$ & $8875$ & $-6.12 \pm 5.91$ \\
        16. & Apoteket & The pharmacy & $-0.267$ & $10085$ & $-6.05 \pm 4.49$ \\
        17. & Maven & The stomach & $-0.267$ & $42105$ & $-2.36 \pm 2.82$ \\
        18. & Psykiatrisk & Psychiatric & $-0.263$ & $3688$ & $-8.99 \pm 8.49$ \\
        19. & Lungebetændelse & Pneumonia & $-0.231$ & $7597$ & $-5.79 \pm 5.62$ \\
        20. & Mavesmerter & Stomach pain & $-0.209$ & $10551$ & $-5.12 \pm 4.02$ \\
        21. & Afføring & Stool & $-0.199$ & $19155$ & $-3.40 \pm 3.27$ \\
        22. & Ribbenene & The ribs & $-0.195$ & $3928$ & $-8.26 \pm 6.18$ \\
        23. & Bløde & Bleed & $-0.194$ & $10501$ & $-4.88 \pm 3.97$ \\
        24. & Bløder & Bleeding & $-0.193$ & $24313$ & $-2.90 \pm 2.93$ \\
        25. & Ribben & Ribs & $-0.189$ & $2941$ & $-8.96 \pm 7.56$ \\
        26. & Brækket & Broken & $-0.183$ & $19415$ & $-3.49 \pm 2.83$ \\
        27. & Betændelse & Inflammation & $-0.181$ & $10050$ & $-5.27 \pm 3.30$ \\
        28. & Forkølet & Common cold & $-0.161$ & $8127$ & $-5.31 \pm 3.75$ \\
        29. & Morgen & Morning or morrow & $-0.160$ & $78558$ & $-1.23 \pm 1.70$ \\
        30. & Hævelse & Swelling & $-0.159$ & $17762$ & $-3.71 \pm 2.32$ \\

@@

As we can only assume how call takers are influenced by model predictions (II), precisely evaluating the hypothetical performance of call takers when supported by a machine learning framework is impossible. Furthermore, option 2 may influence the conversation, further complicating matters. Therefore, we report the results combining the call taker and the model under the following two assumptions:
%
\begin{enumerate}[label=\Alph*.]
    \item Call takers change any stroke prediction from negative to positive if the model predicts a positive (call takers mirror model positives).
    \item Call takers change any stroke prediction from positive to negative if the model predicts a negative (call takers mirror model negatives).
\end{enumerate}
%
By definition, method A tended to increase sensitivity and decrease PPV, whereas method B tended to decrease sensitivity and increase PPV.

@@

>>>>

\chapter[supplementary material: a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{Supplementary Material for: A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{app:supplementary-retrospective}
% \ifthenelse{\equal{\skipappendices}{true}}{}{

@@

Let $z^{(n,d)}$ be the logit output of model $n$ for transcript $d$, $t^{(n)}$ be the tuned logit threshold of model $n$, and $N$ be the number of models in the ensemble. The output score $p^{(n)}$ is then given by 
%
\begin{equation}
    p^{(d)} = \frac{1}{N} \sum_{n=1}^N \sigma\left(z^{(n,d)} - t^{(n)}\right) \enspace ,
\end{equation}
%
where $\sigma(\cdot)$ is the sigmoid function (or standard logistic function). The final ensembel predction $s^{(d)}$ is then simply 
%
\begin{equation}
    s^{(d)} = I_{p^{(d)} > 0.5}\left(p^{(d)}\right) \enspace ,
\end{equation}
%
where $I_{\cdot}(\cdot)$ is the indicator function that returns 1 if the subscript condition is satisfied and 0 otherwise.

@@

% \todo[inline]{Insert table A2 here}
\begin{table}[h]
    \centering
    \caption{Model performance for sex and age subgroups [mean (95\% CI)] on the MH-1813 test data when 1-1-2 training data is not used for training.}
    \label{tab_retrospective:tableA2}
    \resizebox*{0.85\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{4}{c|}{Model w/o 1-1-2 training data} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

@@

        F1-score [\%] $\uparrow$ & \makecell[c]{28.7 \\ (27.8-29.6)} & \makecell[c]{36.2 \\ (35.3-37.2)} & \makecell[c]{20.5 \\ (19.5-21.5)} & \makecell[c]{39.4 \\ (38.6-40.3)} \\
        \midrule
        Sensitivity [\%] $\uparrow$ & \makecell[c]{58.2 \\ (56.7-59.9)} & \makecell[c]{62.1 \\ (60.7-63.6)} & \makecell[c]{53.0 \\ (50.9-55.0)} & \makecell[c]{63.0 \\ (61.9-64.3)} \\
        \midrule
        PPV [\%] $\uparrow$ & \makecell[c]{19.0 \\ (18.3-19.7)} & \makecell[c]{25.6 \\ (24.8-26.4)} & \makecell[c]{12.7 \\ (12.0-13.4)} & \makecell[c]{28.7 \\ (27.9-29.5)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - NPV)}  & \makecell[c]{0.077 \\ (0.073-0.080)} & \makecell[c]{0.102 \\ (0.097-0.106)} & \makecell[c]{0.034 \\ (0.032-0.036)} & \makecell[c]{0.318 \\ (0.305-0.331)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell[c]{0.45 \\ (0.446-0.463)} & \makecell[c]{0.483 \\ (0.473-0.494)} & \makecell[c]{0.264 \\ (0.258-0.270)} & \makecell[c]{1.335 \\ (1.308-1.362)} \\

% \todo[inline]{Insert table A3 here}
\begin{table}[h]
    \centering
    \caption{Model performance for sex and age subgroups [mean (95\% CI)] on the 2021 data without diagnostic category.}
    \label{tab_retrospective:tableA3}
    \resizebox*{0.85\textwidth}{!}{%
    \begin{tabular}{l|cc|cc}
        \toprule

         & \multicolumn{4}{c|}{Model} \\
        \midrule
         & Female & Male & 18-64 years & 65+ years \\

@@

        F1-score [\%] $\uparrow$                                 & \makecell[c]{30.4 \\ (29.3-31.5)} & \makecell[c]{35.2 \\ (34.0-36.4)} & \makecell[c]{24.3 \\ (23.0-25.7)} & \makecell[c]{36.6 \\ (35.6-37.6)} \\
        \midrule
        Sensitivity [\%] $\uparrow$                              & \makecell[c]{44.5 \\ (42.9-46.0)} & \makecell[c]{52.8 \\ (51.1-54.4)} & \makecell[c]{45.6 \\ (43.4-47.9)} & \makecell[c]{49.2 \\ (47.9-50.5)} \\
        \midrule
        PPV [\%] $\uparrow$                                      & \makecell[c]{23.1 \\ (22.2-24.1)} & \makecell[c]{26.4 \\ (25.3-27.4)} & \makecell[c]{16.6 \\ (15.5-17.5)} & \makecell[c]{29.1 \\ (28.2-30.0)} \\
        \midrule
        \makecell[l]{FOR [\%] $\downarrow$ \\ (1 - NPV)}         & \makecell[c]{0.152 \\ (0.146-0.159)} & \makecell[c]{0.155 \\ (0.147-0.162)} & \makecell[c]{0.058 \\ (0.055-0.062)} & \makecell[c]{0.372 \\ (0.359-0.386)} \\
        \midrule
        \makecell[l]{FPR [\%] $\downarrow$ \\ (1 - specificity)} & \makecell[c]{0.404 \\ (0.394-0.414)} & \makecell[c]{0.480 \\ (0.467-0.494)} & \makecell[c]{0.246 \\ (0.239-0.254)} & \makecell[c]{0.873 \\ (0.852-0.894)} \\

@@

\begin{table}[h]
    \centering
    \caption{Overall performance on MH-1813 test data for the original model, the model without 1-1-2 training data, and the model without 1813 training data along with call-taker performance [mean (95\% CI)].}
    \label{tab_retrospective:tableA5}
    \resizebox*{0.98\textwidth}{!}{%
    \begin{tabular}{l|ccccc}
        \toprule
        & F1-score [\%] $\uparrow$ & Sensitivity [\%] $\uparrow$ & PPV [\%] $\uparrow$ & \makecell[c]{FOR [\%] $\downarrow$ \\ (1 - NPV)} & \makecell[c]{FPR [\%] $\downarrow$ \\ (1 - specificity)} \\
        \midrule
        & \multicolumn{5}{c}{\textit{Overall}} \\
        \midrule

        Call-takers  & \makecell[c]{25.8 \\ (23.7-27.9)} & \makecell[c]{52,7 \\ (49,2-56.4)} & \makecell[c]{17.1 \\ (15.5-18.6)} & \makecell[c]{0.105 \\ (0.094-0.116)} & \makecell[c]{0.565 \\ (0.539-0.590)} \\
        \midrule
        Model        & \makecell[c]{35.7 \\ (35.0-36.4)} & \makecell[c]{63.0 \\ (62.0-64.1)} & \makecell[c]{24.9 \\ (24.3-25.5)} & \makecell[c]{0.082 \\ (0.079-0.085)} & \makecell[c]{0.419 \\ (0.413-0.426)} \\
        \midrule
        \makecell[l]{Model \\ w/o 1-1-2} & \makecell[c]{32.4 \\ (31.8-33.1)} & \makecell[c]{60.4 \\ (59.3-61.4)} & \makecell[c]{22.2 \\ (21.6-22.7)} & \makecell[c]{0.088 \\ (0.085-0.091)} & \makecell[c]{0.467 \\ (0.460-0.474)} \\
        \midrule
        \makecell[l]{Model \\ w/o MH-1813} & \makecell[c]{31.4 \\ (30.7-32.1)} & \makecell[c]{50.4 \\ (49.3-51.4)} & \makecell[c]{22.8 \\ (22.2-23.4)} & \makecell[c]{0.110 \\ (0.106-0.113)} & \makecell[c]{0.375 \\ (0.369-0.381)} \\

        % & \multicolumn{5}{c}{\textit{Without 1-1-2 training data (only MH-1813 data)}} \\
        % \midrule
        % Model        & \makecell[c]{32.4 \\ (31.8-33.1)} & \makecell[c]{60.4 \\ (59.3-61.4)} & \makecell[c]{22.2 \\ (21.6-22.7)} & \makecell[c]{0.088 \\ (0.085-0.091)} & \makecell[c]{0.467 \\ (0.460-0.474)} \\

        % & \multicolumn{5}{c}{\textit{Without MH-1813 training data (only 1-1-2 data)}} \\
        % \midrule
        % Model        & \makecell[c]{31.4 \\ (30.7-32.1)} & \makecell[c]{50.4 \\ (49.3-51.4)} & \makecell[c]{22.8 \\ (22.2-23.4)} & \makecell[c]{0.110 \\ (0.106-0.113)} & \makecell[c]{0.375 \\ (0.369-0.381)} \\

@@

In \cref{tab_retrospective:tableA6,tab_retrospective:tableA7} we provide detailed versions of the data presented in the model explainability section in the main manuscript. Specifically, we include the Danish word, its English translation, the rank and impact scores and the number of occurrences of each word.

% % \todo[inline]{Insert table A4 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest positive rank score in calls predicted as stroke.}
    \label{tab_retrospective:tableA6}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llccc}
        \toprule
        \multicolumn{6}{c}{Stroke predictions, $D=1,897$} \\
        \midrule
         & \makecell{Word, $w$ \\ (\textit{Danish})} & \makecell{Translation, $w$ \\ (\textit{English})} & Rank, $r^{(w)}$ & Count, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Ambulance & Ambulance & $1.000$ & $1,$680 & $0.52 \pm 0.51$ \\
        2. & Blodprop & Blood clot & $0.599$ & $89$5 & $0.51 \pm 0.58$ \\
        3. & Venstre & Left & $0.381$ & $1,$108 & $0.38 \pm 0.4$ \\
        4. & Højre & Right & $0.326$ & $1,$050 & $0.31 \pm 0.42$ \\
        5. & Dobbeltsyn & Double vision & $0.247$ & $84$ & $1.01 \pm 1.26$ \\
        6. & Ordene & The words & $0.217$ & $34$4 & $0.6 \pm 0.45$ \\
        7. & Pludselig & Suddenly & $0.142$ & $78$3 & $0.29 \pm 0.28$ \\
        8. & Arm & Arm & $0.140$ & $70$9 & $0.3 \pm 0.3$ \\
        9. & Side & Side & $0.125$ & $1,$139 & $0.23 \pm 0.21$ \\
        10. & Apopleksi & Stroke & $0.102$ & $11$7 & $0.33 \pm 0.82$ \\
        11. & Dobbelt & Double & $0.102$ & $11$3 & $0.54 \pm 0.72$ \\
        12. & Styre & Control & $0.092$ & $13$4 & $0.63 \pm 0.46$ \\
        13. & Opkald & Call & $0.067$ & $39$ & $0.18 \pm 1.22$ \\
        14. & Følelsesløs & Numb & $0.065$ & $94$ & $0.53 \pm 0.58$ \\
        15. & Minutter & Minutes & $0.064$ & $76$3 & $0.22 \pm 0.16$ \\
        16. & Talebesvær & Difficulties speaking & $0.063$ & $44$ & $0.87 \pm 0.72$ \\
        17. & Hjerneblødning & Haemorrhagic stroke & $0.060$ & $13$3 & $0.4 \pm 0.49$ \\
        18. & Hånd & Hand & $0.057$ & $29$7 & $0.28 \pm 0.31$ \\
        19. & Ambulancen & The ambulance & $0.055$ & $52$1 & $0.21 \pm 0.23$ \\
        20. & Snøvler & Slurred speech & $0.052$ & $58$ & $0.71 \pm 0.54$ \\
        21. & Blodpropper & Blood clots & $0.051$ & $22$4 & $0.27 \pm 0.36$ \\
        22. & Hurtigt & Fast & $0.048$ & $66$3 & $0.18 \pm 0.18$ \\
        23. & Udtrykke & Express & $0.044$ & $44$ & $0.59 \pm 0.74$ \\
        24. & Blodfortyndende & Blood thinner & $0.044$ & $25$9 & $0.32 \pm 0.22$ \\
        25. & Usammenhængende & Incoherent & $0.043$ & $15$ & $1.14 \pm 1.13$ \\
        26. & Skæv & Lopsided & $0.039$ & $21$1 & $0.29 \pm 0.28$ \\
        27. & Nedsat & Reduced & $0.038$ & $52$8 & $0.14 \pm 0.21$ \\
        28. & Hænger & Hangs & $0.036$ & $62$8 & $0.15 \pm 0.17$ \\
        29. & Forbigående & Transient & $0.035$ & $48$ & $0.52 \pm 0.62$ \\
        30. & Vrøvler & Not making sense & $0.033$ & $14$ & $1.13 \pm 0.89$ \\
        \bottomrule
    \end{tabular}%
    }
\end{table}

% \todo[inline]{Insert table A5 here}
\begin{table}[h]
    \centering
    \caption{Mean impact for words with the largest negative rank score in calls predicted as non-stroke.}
    \label{tab_retrospective:tableA7}
    \resizebox*{\textwidth}{!}{%
    \begin{tabular}{l|llcrr}
        \toprule
        \multicolumn{6}{c}{Non-stroke predictions, $D=342,133$} \\
        \midrule
         & \makecell{Word, $w$ \\ (\textit{Danish})} & \makecell{Translation, $w$ \\ (\textit{English})} & Rank, $r^{(w)}$ & Count, $D^{(w)}$ & \makecell{Impact, $i^{(d,w)}$ \\ mean $\pm$ std.} \\
        \midrule    
        1. & Stivkrampe & Tetanus & $-1.000$ & $4378$ & $-19.40 \pm 10.61$ \\
        2. & Gravid & Pregnant & $-0.901$ & $8749$ & $-12.08 \pm 8.64$ \\
        3. & Skåret & Cut & $-0.772$ & $7592$ & $-11.98 \pm 8.61$ \\
        4. & Forbinding & Bandage & $-0.569$ & $4561$ & $-12.87 \pm 10.08$ \\
        5. & Amager & Amager (a location) & $-0.566$ & $23776$ & $-5.60 \pm 4.43$ \\
        6. & Klokken & O'clock & $-0.535$ & $94436$ & $-2.22 \pm 2.69$ \\
        7. & Skadestuen & The emergency room & $-0.486$ & $42809$ & $-3.72 \pm 3.23$ \\
        8. & Politiet & The police & $-0.413$ & $2903$ & $-10.73 \pm 13.77$ \\
        9. & Hævet & Swollen & $-0.388$ & $60559$ & $-2.84 \pm 2.38$ \\
        10. & Håndkøb & over the counter (otc) & $-0.372$ & $4641$ & $-11.64 \pm 6.00$ \\
        11. & Halsen & The neck & $-0.366$ & $30151$ & $-3.33 \pm 3.86$ \\
        12. & Feber & Fever & $-0.361$ & $112586$ & $-1.94 \pm 1.76$ \\
        13. & Recept & Prescription & $-0.334$ & $5450$ & $-9.87 \pm 5.82$ \\
        14. & Centimetre & Centimetre & $-0.311$ & $12026$ & $-6.01 \pm 4.39$ \\
        15. & Knæet & The knee & $-0.300$ & $8875$ & $-6.12 \pm 5.91$ \\
        16. & Apoteket & The pharmacy & $-0.267$ & $10085$ & $-6.05 \pm 4.49$ \\
        17. & Maven & The stomach & $-0.267$ & $42105$ & $-2.36 \pm 2.82$ \\
        18. & Psykiatrisk & Psychiatric & $-0.263$ & $3688$ & $-8.99 \pm 8.49$ \\
        19. & Lungebetændelse & Pneumonia & $-0.231$ & $7597$ & $-5.79 \pm 5.62$ \\
        20. & Mavesmerter & Stomach pain & $-0.209$ & $10551$ & $-5.12 \pm 4.02$ \\
        21. & Afføring & Stool & $-0.199$ & $19155$ & $-3.40 \pm 3.27$ \\
        22. & Ribbenene & The ribs & $-0.195$ & $3928$ & $-8.26 \pm 6.18$ \\
        23. & Bløde & Bleed & $-0.194$ & $10501$ & $-4.88 \pm 3.97$ \\
        24. & Bløder & Bleeding & $-0.193$ & $24313$ & $-2.90 \pm 2.93$ \\
        25. & Ribben & Ribs & $-0.189$ & $2941$ & $-8.96 \pm 7.56$ \\
        26. & Brækket & Broken & $-0.183$ & $19415$ & $-3.49 \pm 2.83$ \\
        27. & Betændelse & Inflammation & $-0.181$ & $10050$ & $-5.27 \pm 3.30$ \\
        28. & Forkølet & Common cold & $-0.161$ & $8127$ & $-5.31 \pm 3.75$ \\
        29. & Morgen & Morning or morrow & $-0.160$ & $78558$ & $-1.23 \pm 1.70$ \\
        30. & Hævelse & Swelling & $-0.159$ & $17762$ & $-3.71 \pm 2.32$ \\

@@

As we can only assume how call takers are influenced by model predictions (II), precisely evaluating the hypothetical performance of call takers when supported by a machine learning framework is impossible. Furthermore, option 2 may influence the conversation, further complicating matters. Therefore, we report the results combining the call taker and the model under the following two assumptions:
%
\begin{enumerate}[label=\Alph*.]
    \item Call-takers change any stroke prediction from negative to positive if the model predicts a positive (call takers mirror model positives).
    \item Call-takers change any stroke prediction from positive to negative if the model predicts a negative (call takers mirror model negatives).
\end{enumerate}
%
By definition, method A tended to increase sensitivity and decrease PPV, whereas method B tended to decrease sensitivity and increase PPV.

@@

\section{Research in context search term results}
The search terms stroke AND (artificial intelligence OR machine learning OR deep learning) AND (EMS OR emergency medical services OR dispatch OR telephone) yielded 88 articles in PubMed. These articles are listed below:

{\small
\begin{enumerate}
    \item Soun JE, Chow DS, Nagamine M et al. Artificial intelligence and acute stroke imaging. AJNR. American journal of neuroradiology 2021; 42: 2-11.
    \item Murray NM, Unberath M, Hager GD, Hui FK. Artificial intelligence to diagnose ischemic stroke and identify large vessel occlusions: a systematic review. Journal of neurointerventional surgery 2020; 12: 156-64.
    \item Shlobin NA, Baig AA, Waqas M et al. Artificial intelligence for large-vessel occlusion stroke: a systematic review. World neurosurgery 2022; 159: 207-20.e1.
    \item Linder SM, Rosenfeldt AB, Bay RC, Sahu K, Wolf SL, Alberts JL. Improving quality of life and depression after stroke through telerehabilitation. The American journal of occupational therapy: official publication of the American Occupational Therapy Association 2015; 69: 6902290020p1-10.
    \item Humphreys K, Shover CL, Andrews CM et al. Responding to the opioid crisis in North America and beyond: recommendations of the Stanford-Lancet Commission. Lancet (London, England) 2022; 399: 555-604.
    \item Fassbender K, Lesmeister M, Merzou F. Prehospital stroke management and mobile stroke units. Current opinion in neurology 2023; 36: 140-6.
    \item McDonough RV, Ospel JM, Majoie CBLM et al. Clinical outcome of patients with mild pre-stroke morbidity following endovascular treatment: a HERMES substudy. Journal of neurointerventional surgery 2023; 15: 214-20.
    \item Bat-Erdene BO, Saver JL. Automatic acute stroke symptom detection and emergency medical systems alerting by mobile health technologies: a review. Journal of stroke and cerebrovascular diseases: the official journal of National Stroke Association 2021; 30: 105826.
